Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-01 analysis/paper/paper.Rmd
use same terminology "index values"

p <- ggplot(rrpp_long, aes(x = as.factor(value))) +
  geom_bar(fill = "black") +
  ylab("Count") +
  xlab("Article Score") +
  ggtitle("Reproducibility criteria ranks") +
  facet_wrap(name ~ .)
p <- tag_facet(
  p = p,
  tag_pool = LETTERS,
  x = 5,
  family = "Arial",
  open = "",
  close = ""
)

>>>>

p <- ggplot(rrpp_long, aes(x = as.factor(value))) +
  geom_bar(fill = "black") +
  ylab("Count") +
  xlab("Article Score") +
  ggtitle("Reproducibility criteria index values") +
  facet_wrap(name ~ .)
p <- tag_facet(
  p = p,
  tag_pool = LETTERS,
  x = 5,
  family = "Arial",
  open = "",
  close = ""
)
